---
title: "IRGA data for NCOS"
author: "Jacob Weverka"
date: "7/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading necessary libraries

```{r, message=FALSE}
library(tidyverse)
library(magrittr)
library(R.utils)
library(broom)
library(here)
# library(BAS)
```


 <font size="4">  General setup 4</font>


Read in licor data with timestamp and date

```{r, message = FALSE}
# raw data folder
licor_raw = here::here("data/maggie_licor_raw/")

# list of files in raw data folder
files = list.files(licor_raw)


run_data = tibble(filename = files) %>%
  mutate(contents = map(filename, ~ read_table2(file.path(licor_raw, .x), skip = 1) %>%
                          rename(time = `Time(H:M:S)`))) %>%
  mutate(timestamp_date = map(filename, ~ (str_remove(strsplit(readLines(con = file.path(licor_raw, .x), n = 1), split = " ")[[1]][1], '"'))) %>%
           lubridate::ymd(),
         timestamp_time = map(filename, ~ read_table2(file.path(licor_raw, .x), skip = 1)[1,1])) %>%
  unnest(timestamp_time)

```
Read in sequence data from lab

```{r, message=FALSE}

# excel files (CSV) with sample info folder
sequence_files = here::here("data/maggie_sample_sequences/")

seqs = list.files(sequence_files)

date_fun = function(df){df$date[1]}

time_fun = function(df){df$time[1]}

all_seqs = tibble(filename = seqs) %>%
  mutate(sequences = map(filename, ~ read_csv(file.path(sequence_files, .x)) %>% 
                           dplyr::filter(height > baseline) %>% 
                           mutate(peak_number = seq.int(nrow(.)))
                         )) %>% 
  mutate(timestamp_date = lubridate::mdy(map(sequences, date_fun)),
         timestamp_time = map(sequences, time_fun))

```


Add time elapsed within nested data
Filter out non-peak data
Assign peaks

```{r}
baseline = 5

run_data = run_data %>%
  mutate(contents = map(contents,
                       ~ mutate(.x,
                                time_elapsed = seq.int(nrow(.)),
                                is_peak = `CO2(ppm)` > baseline)
                       )
         ) %>%
  unnest(contents) %>%
  filter(is_peak) %>%
  nest(-filename, -timestamp_date, -`Time(H:M:S)`) %>%
    mutate(data = 
           map(data, ~
             .x %>% mutate(peak_number = cumsum((time_elapsed - lag(time_elapsed)) > 1 & !is.na(lag(time_elapsed))) + 1
                      )
           )
  )

```

Calculate area under the curve


```{r message=FALSE, warning=FALSE}
calc_area = function(df){ as.double(sum(df$rectangle, na.rm = TRUE) + sum(df$triangle, na.rm = TRUE))}

intp = run_data %>%
  mutate(data = map(data, ~ .x %>%
                      nest(-peak_number) %>%
                      mutate(data = map(data, ~ .x %>%
                                          add_row %>%
                                          mutate(
                                            rectangle = `CO2(ppm)`,
                                            triangle = abs(diff(c(baseline[1], `CO2(ppm)`[!is.na(`CO2(ppm)`)], baseline[1]))) * 0.5
                                            )
                                        )
                             ) %>%
                      mutate(area = map(data, calc_area) %>% flatten_dbl()) %>%
                      filter(area > 15) %>%
                      mutate(peak_number = seq.int(nrow(.)))
                    ),
         timestamp_date = lubridate::ymd(timestamp_date)
         )
```
Join sequence data to licor data

```{r}
all_data =
  inner_join(all_seqs, intp, by = "timestamp_date")
```




Joining data - be aware if you have multiple files for the same date it will produce all possible combos for that row

```{r}
all_data = as_tibble(intp) %>%
  inner_join(as_tibble(all_seqs), by = "timestamp_date") %>%
  mutate(labeled_data = map2(.x = data, .y = sequences, ~ left_join(.x, .y, by = "peak_number")),
         standards = map(labeled_data, ~ .x %>% drop_na(std)),
         samples = map(labeled_data, ~ .x %>% filter(is.na(std))))
```


Make standard curve

```{r message = FALSE}
add_sc = all_data %>% 
  mutate(fit = map(standards, ~ lm(std_conc ~ 0 + area, data = .)),
         results = map(fit, tidy),
         pval = map2(fit, results, ~ glance(.x) %>%
                      select(r.squared) %>%
                      bind_cols(.y$p.value)))
```


Calculate ppm values with confidence intervals for samples

```{r}
finished = add_sc %>%
  mutate(samples = map2(fit, samples,
                       ~ .y %>% bind_cols(as.data.frame(predict(.x, .y, interval = "confidence"))))
  ) %>%
  arrange(timestamp_date)
```


```{r}

```

